---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# asciiConverter

<!-- badges: start -->
<!-- badges: end -->

The asciiConverter package aims to provide users with a tool that is both creative and simple in reconstructing regular text into a 
fun ASCII art text that is bolded and block styled. Users will be able to input text through multiple sources including directly from 
the R terminal, from .txt files, and potentially from .csv files. The package will then output the stylized block text either into the 
terminal or into the text files. Our goal for this package is to build a visually appealing and striking text that will be an easy tool 
for users as well as versatile. This will allow for users to edit and customize the output while also providing multiple input and output 
options. The package can be useful in building creative messaging for message, headers, or designs within the user's console, application, 
report, or other academic tools.

Some of the key components of this package include functions that are able to convert individual letters into the ASCII block format. 
Beginning with mapping letters to numeric values that will determine how each letter character will be constructed. From there, these 
functions will be flexible, allowing for users to read text from different sources, convert it into block text, and write the output into 
a terminal or file. Through combining these functions, the asciiConverter brings forth an efficient and organized tool to help turn 
regular text into fun, fancy, block style text that will be fast, easy, accessible, and user friendly allowing for a new creative tool in coding. 


## Installation

You can install the development version of asciiConverter from [GitHub](https://github.com/Lydia-Blackwell-Esslami/asciiConverter) with:


``` r
# install.packages("pak")
pak::pak("Lydia-Blackwell-Esslami/asciiConverter")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(asciiConverter)
## basic example code
```

